%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Vishal Gupta} \\ \vspace{1pt}
    \small +91 7019725607 $|$ \href{mailto:vishalguptasnwl@gmail.com}{\underline{vishalguptasnwl@gmail.com}} $|$
    \href{https://linkedin.com/in/vishal-gupta-09886599}{\underline{linkedin.com/in/vishal-gupta-09886599}} $|$
    \href{https://github.com/vishalguptasnwl}{\underline{github.com/vishalguptasnwl}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {RNS Institute of Technology}{Bengaluru, Karnataka}
      {Bachelor of Engineering in Computer Science}
      {Apr. 2013 -- May 2017}
    \resumeSubheading
      {DAV Public School}{Bokaro, Jharkhand}
      {12th PCM}{Mar. 2011 -- Mar 2013}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Test Associate Senior Engineer(Python Automation)}{Oct 2018 -- Present}
      {SonicWall India Pvt Ltd}{Bengaluru, Karnataka}
      \resumeItemListStart
      \item[] \textbf{{Email Security} {(Oct 2018 - Present)}}
        \resumeItem{Designed and developed Python REST API automation framework, using unittest, built on the design of "Library Architecture Testing", with advantages of code reusability, scalability and low-cost maintenance.}
        \resumeItem{Worked on architecture and moving Email Security integrated server CASS(Comprehensive Anti Spam Service) from self-maintenance servers to AWS.}
        \resumeItem{Worked on performance analysis of Email Security product using IXIA traffic generator tool by taking time several parameters and identifying bottlenecks.}
      \resumeItemListEnd
      
       \resumeItemListStart
      \item[] \textbf{{NSM: Network Security Manager} {(Feb 2020 - Nov 2020)}}
        \resumeItem{Worked on REST-API Automation, Optimization of scripts and part of the framework development team developed on python. Provided ideas for optimizing the framework to reduce code.}
        \resumeItem{Automated multiple features using API from smoke to regression which helped the application to manage multiple firewalls at several location seamlessly.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Associate Software Engineer}{Mar. 2018 -- Jun, 2018}
      {Accenture Technology Pvt Ltd}{Bengaluru, Karnataka}
      \resumeItemListStart
        \resumeItem{Developed prototype models on solution of Industrial IoT.}
        \resumeItem{Part of 15 selected engineers for the digital training team from India and got training on IoT technologies. Learned various technologies related to IoT.}
    \resumeItemListEnd
  \resumeSubHeadingListEnd
%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, SQL , HTML/CSS} \\
     \textbf{Cloud}{: AWS(ec2, load-balancing, Network Configuration), Azure(Active Directory)} \\
     \textbf{Tools}{: Perforce, Git, Wireshark, Swagger UI, Postman, IXIA, JIRA} \\
     \textbf{Libraries}{: pandas, NumPy, Matplotlib}\\
     \textbf{Protocols}{: UDP, TCP, IPV4, IPV6, HTTP, DHCP, SMTP, SNMP, IMAP, POP3, TLS, SSL, ICMP, LDAP, DNS, FTP} \\
    }}
 \end{itemize}

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Gitlytics} $|$ \emph{Python, Flask, React, PostgreSQL, Docker}}{}
          \resumeItemListStart
            \resumeItem{Developed a full-stack web application using with Flask serving a REST API}
            \resumeItem{Implemented GitHub OAuth to get data from user’s repositories}
            \resumeItem{Visualized GitHub data to show collaboration}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------AWARDS AND CERTIFICATIONS-----------
\section{Awards and Certifications}
 \begin{itemize}[leftmargin=0.15in, label={}]
  \item{* Awarded for “2019-Key-Contributor(Email Security)” at Sonicwall Technology Systems, Bengaluru, India.}\\
   {* National Programme on Technology Enhanced Learning (NPTEL) online certification in “Information Security -3” by 
Indian Institute of Technology-Madras. (an initiative by Ministry of Human Resources and Development (MHRD), India).}\\{* Participated in the “Game Development Workshop” held at the Indian Institute of Science.}
 \end{itemize}
%-------------------------------------------
\end{document}
